\section{Observables and Measurements}
As much fun as it might be to manipulate a quantum state, we also have to measure it and how it connects to the properties of the system at hand. Any given physical quantity $A$ is associated with a Hermitian operator $\hat{A} = \hat{A}^\dag$ acting in the Hilbert space of the system, which we defined previously. Please, be utterly aware that those Hermitian operators have absolutely no need to be unitary. However, any unitary operator might be written as $\hat{U}= e^{i\hat{A}}$.

In a \emph{measurement} , the possible outcomes are then the eigenvalues $a_\alpha$ \index{eigenvalue} of the operator $\hat{A}$:

\begin{align}
	\hat{A}\ket{\alpha}=a_{\alpha}\ket{\alpha}.
\end{align}
The system will collapse to the corresponding eigenvector and the probability of finding the system in state $\ket{\alpha}$ is
\begin{align}
	P(\ket{\alpha})=||\hat{P}_{\ket{\alpha}} \ket{\psi}||^2 = \bra{\psi} \hat{P}^{\dag}_{\ket{\alpha}} \hat{P}_{\ket{\alpha}} \ket{\psi},
\end{align}
where $\hat{P}_{\ket{\alpha}}= \ket{\alpha} \bra{\alpha}$.

As for our previous examples, how would you measure them typically, i.e. what would be the operator ?
\begin{enumerate}
\item The operator to be tested is the position operator of the electron bound to the nucleus. We access it indirectly through spectroscopy.
\item For the occupation number we have nowadays number counting photodectors.
\item The position of an atom might be detected through high-resolution CCD cameras.
\item For the arm of the interferometer we will typically measure the output through photodetectors...
\item For the \textit{measurement of the spin}, we typically correlate the internal degree of freedom to the spatial degree of freedom. This is done by applying a magnetic field gradient acting on the magnetic moment $\hat{\vec{\mu}}$ \index{magnetic moment}, which in turn is associated with the spin via $\hat{\vec{\mu}} = g \mu_B \hat{\vec{s}}/\hbar$, where $g$ is the Landé $g$-factor \index{Land\'e $g$-factor} and $\mu_B$ is the Bohr magneton \index{Bohr magneton}. The energy of the system is $\hat{H} = -\hat{\vec{\mu}} \cdot \vec{B}$.
\end{enumerate}